HCI Project Proposal and Preliminary Literature Review

### 2015-10-08 sigchi-latex-proceedings 2/proceedings.tex
minor fixes for ishan.

As smartphone technology has evolved, multitasking is now supported on many mobile devices. This allows users to have many applications (apps) running at once and switch between them to save start up time and save state in a given app. Unlike PCs, screen real estate is much smaller on smartphones, meaning, for most devices, only one app can be in the foreground. The ability to have one app open and save state while launching another app is becoming important for users to use their devices.

@@

Leiva [2] explored different techniques to improve task resumption time in a multi-tab browser environment. Multitasking over different types of tasks can reduce productivity, lead to more errors and contrary to what we might expect, lead to a higher task completion time [2]. The study investigated the effects of a tool designed to remind users of their position on the screen prior to app switching, as well as the last interacted element and cursor position. The use of this tool improved task resumption time and task completion time. In our research we will attempt remind users of their task state using this proposed method.

>>>>

As smartphone technology has evolved, multitasking is now supported on many mobile devices. This allows users to have many applications (apps) running at once and switch between them to save start up time and save state in a given app. Unlike PCs, screen real estate is much smaller on smartphones, meaning, for most devices, only one app can be in the foreground. The ability to have one app open and save state while using another app is becoming increasingly important for users get the most out of their devices.

@@

Leiva [2] explored different techniques to improve task resumption time in a multi-tab browser environment. Multitasking over different types of tasks can reduce productivity, lead to more errors and contrary to what we might expect, lead to a higher task completion time [2]. The study investigated the effects of a tool designed to remind users of their position on the screen prior to app switching, as well as the last interacted element and cursor position. The use of this tool improved task resumption time and task completion time.
